### 2019-07-25 manuscript.tex
Update manuscript.tex

It is estimated, based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, 44 million are girls below age 15.  It was also foreseen that another 15 million girls and women are at risk by 2020  \cite{AdnrLesc16, UNIC16}.  Progress in reducing FGC is not keeping up with the population growth: the number of girls and women undergoing FGC is projected to rise significantly over the next decade if current trends continue \cite{KhosBane17, UNIC16}.  Following Tostan \cite{Tost15}, we used cutting instead of circumcision without demising or excusing the negative impact of the practice while recognizing a sense of self-awareness in FAC decision\cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}. \cfonly{less cites}

In most part of the world, FGC is defined as violating human rights \cite{WHO97, WHO08} \cfonly{add and update}.  The commonly shared position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.  Progress of intervention is hindered because of the complicated history \cite{BergDeni12, Cami16}.  FGC is embodied with multiple perspectives from cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}. \cfonly{too many cites}.  Understanding values attached to FGC is essential to comprehend the persistence of FGC practice \cite{Bicc10}.  Social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, presents a crucial venue in comprehending intervention of sustainable changes \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.

It was found that FGC values and norms tended to be deeply internalized and morally embraced \cite{SchuLien13}.  Social convention theory, a leading theory utilizing normative behavior in FGC research \cite{Hayf05, ShelWand11} \cfonly{more} proposed that FGC was a marriageability convention and extending to, latter, a social norm, such as religious obligation, adolescent rite of passage, and female honour and modesty as an important norm to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.   FGC was furthered deemed as a form of social capital, a value expected by women for inclusion within women’s social groups \cite{ShelWand11}. The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11}.  Basically, when the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}.  Although normative behaviour based on convention theory was well documented regarding analysis of persistence of FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), it was not without challenges \cite{EffeVogt15, Njam04}.  \cfonly{adding Bicchiori, The planned behaviour etc}For example, there was no coordination game observed in marital expectation \cite{EffeVogt15} and it was a peer convention for inclusion instead of for marriageability \cite{ShelWand11}.   It was also argued that anti-FGC discourse perpetuated a colonial assumption by universalizing a western view of normal body and sexuality \cite{Njam04}.  Studies showed that factors other than marriageability have underlined women’s  decisions of FGC \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.

@@

In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?}.  Cluster  was used as a proxy to represent a community level of impact \cite{AligRen06, Hayf05, Krav02}

>>>>

Female genital cutting (FGC), circumcision or mutilation is mostly defined as violating human rights \cite{WHO97, WHO08} \cfonly{add and update}.  The commonly shared position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.  It is estimated, based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, 44 million are girls below age 15.  It was also foreseen that another 15 million girls and women are at risk by 2020  \cite{AdnrLesc16, UNIC16}.  Progress of intervention is hindered because of the complicated history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}.  Following Tostan \cite{Tost15}, we used cutting instead of circumcision without demising or excusing the negative impact of the practice while recognizing a sense of self-awareness in FAC decision\cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}. \cfonly{less cites}

FGC is embodied with multiple perspectives from cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, McCh15, SchuLien13, WHO12}. \cfonly{too many cites}.  Understanding reasons and values people attached to FGC is essential to comprehend the persistence of the practice \cite{Bicc10, CislHeis18, Mack96} for any negotiation and to reduce possible harmful intervention \cite{Cami15}.  Social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15}; it can refer to an average outcome or a common practice \cite{MillPrin16}.   Social norms is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a, MillPrin16, MollRima10, RimaLapi15}, provides a crucial venue in negotiating sustainable changes of FGC practice \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.

FGC values and norms tended to be deeply internalized and morally embraced \cite{SchuLien13}.  Social convention theory, a leading theory (e.g., \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}) utilizing normative behavior in FGC research \cite{Hayf05, ShelWand11} \cfonly{more} proposed that FGC was a marriageability convention and extending to, latter, a social norm, such as religious obligation, adolescent rite of passage, and female honour and modesty to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.   FGC was furthered deemed as a form of social capital, a value expected by women for inclusion within their social groups \cite{ShelWand11}. The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11}.  Social expectation (i.e., what other people do or what other people believe one should do) was strongly correlated with FGC practice \cite{BiccMari15}.  Basically, when the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}.

======The planned behaviour \cite{}.  For example, there was no coordination game observed in marital expectation \cite{EffeVogt15} and it was a peer convention for inclusion instead of for marriageability \cite{ShelWand11}.   It was also argued that anti-FGC discourse perpetuated a colonial assumption by universalizing a western view of normal body and sexuality \cite{Njam04}.  Studies showed that factors other than marriageability have underlined women’s  decisions of FGC \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.  =====

@@

Community-based intervention can be effective \cite{CislHeis18}.  In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?}.  Cluster  was used as a proxy to represent a community level of impact \cite{AligRen06, Hayf05, Krav02}
